Relation of severe COVID-19 in Scotland to transmission-related factors and risk conditions eligible for shielding support: REACT-SCOT case-control study

### 2021-04-16 shielding.Rmd
updates to vax efficacy in shielded

header-includes:
  \usepackage{newunicodechar}
  \let\origquote\quote
  \def\quote{\origquote\itshape}
  \usepackage{graphicx}
  \usepackage{geometry}
  \usepackage{longtable}
  \usepackage{booktabs}
  \usepackage{float}
  \floatplacement{figure}{H}
  \usepackage{array}
  \usepackage{threeparttable}
  \usepackage{longtable}
  \usepackage{lscape}
  \usepackage{pdfpages}
  \linenumbers 
output:
  rticles::nejm_article:
    includes:
      in_header: ./preamble.tex
    latex_engine: lualatex
    keep_tex: true
    fig_caption: yes
#    number_sections: false
    md_extensions: -autolink_bare_uris
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
bibliography: ./covid.bib
csl: ./biomed-central.csl
always_allow_html: true
urlcolor: blue
linenumbers: false
linkcolor: cyan

@@

@@

### Association with recent exposure to hospital
A striking finding  from our analysis is the  large risk ratio and PARF for severe disease associated with  exposure to hospital.   Across the epidemic we estimate that the PARF for hospital exposure  using our definition was  30-50% of severe cases.    Although we had pre-specified our exposure variable to include day case and outpatients the association was driven by inpatient hospital exposure.  The PARF associated with inpatient exposure was   `r round(100 * parf.rapid)`%,  Using the accepted international definitions of probable or definite nosocomial acquisition gives a much lower estimate of the PARF .  As we have shown most of this difference is due to the fact that the international definition does not attempt to quantify cases diagnosed shortly after discharge that could have been acquired in hospital.   The other difference  is that the  international definition classifies  those with onset 5-6 days after admission as indeterminate.  As the average incubation period for COVID-19 is 5-6 days we consider it is reasonable  to include exposure in this time window as relevant.

>>>>

header-includes:
  \usepackage{newunicodechar}
  \let\origquote\quote
  \def\quote{\origquote\itshape}
  \usepackage{graphicx}
  \usepackage{geometry}
  \usepackage{longtable}
  \usepackage{booktabs}
  \usepackage{float}
  \floatplacement{figure}{H}
  \usepackage{array}
  \usepackage{threeparttable}
  \usepackage{longtable}
  \usepackage{lscape}
  \usepackage{pdfpages}
output:
  rticles::nejm_article:
    includes:
      in_header: ./preamble.tex
    latex_engine: lualatex
    keep_tex: true
    fig_caption: yes
#    number_sections: false
    md_extensions: -autolink_bare_uris
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
bibliography: ./covid.bib
csl: ./biomed-central.csl
always_allow_html: true
urlcolor: blue
linenumbers: false
linkcolor: cyan

@@

\nolinenumbers

@@

### Association with recent exposure to hospital
A striking finding  from our analysis is the  large risk ratio and PARF for severe disease associated with  exposure to hospital.   Across the epidemic we estimate that the PARF for hospital exposure  using our definition was  30-50% of severe cases.    Although we had pre-specified our exposure variable to include day case and outpatients the association was driven by inpatient hospital exposure.  The PARF associated with inpatient exposure was   `r round(100 * parf.rapid)`%.  Using the accepted international definitions of probable or definite nosocomial acquisition gives a much lower estimate of the PARF.  As we have shown most of this difference is due to the fact that the international definition does not attempt to quantify cases diagnosed shortly after discharge that could have been acquired in hospital.   The other difference  is that the  international definition classifies  those with onset 5-6 days after admission as indeterminate.  As the average incubation period for COVID-19 is 5-6 days we consider it is reasonable  to include exposure in this time window as relevant.
